### 2024-02-07 README.Rmd
add a logo and change theme

<!-- <img src="man/figures/logo.png" align="right" height="240"/> -->
<!-- # sfislands <a href="https://horankev.github.io/sfislands/"><img src="man/figures/logo.png" align="right" height="240" alt="sfislands website" /></a> -->

@@

@@

>>>>

@@

<img src="man/figures/logo.png" align="right" height="240"/>

@@

```{r, fig.width=12, fig.height=6}

prep_data3 <- st_bridges(uk_election, "constituency_name") # decide upon the contiguities and add them to the df

model <- gam(con_swing ~ 
               s(region, bs="re") + # region level random intercept
               s(county, bs="re") + # county level random intercept
               s(county, degree_educated, bs="re") + # county level random coefficient
               s(constituency_name, bs='mrf', 
                 xt=list(nb=prep_data3$nb),k=10) + # ICAR constituency ICAR varying coefficients
               s(constituency_name, by=white, bs='mrf', 
                 xt=list(nb=prep_data3$nb),k=10), # ICAR constituency ICAR varying coefficients
             data=prep_data3, method="REML") |> 
  st_augment(prep_data3) |> # pipe into function to get estimates
  st_quickmap_preds() # pipe into this for visualisation

ggarrange(plotlist = model, legend = "none", nrow=1)
```
